How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-23 tex/dtree.tex
Updates from ShareLaTeX

\begin{figure}[t]
	\small
	~\hrule~

	{\bf Step 1: Distinguish between clusters using  decision trees}

	Use an entropy-based
	decision tree (DT) learner to learn what attributes select for a given data. To limit tree size:
	\bi
	\item Only use the top $\alpha=33$\%  of the features, as determined by their information gain~\cite{Irani1993}. 
	\item Only build the trees down to  max depth of $\beta=10$.
	\item Only build subtrees if it contains at least $N^{\gamma=0.5}$ examples (where $N$ is the size of the training set).
	\ei
	{\em Score}  DT  leaf nodes  via the mean score of its majority cluster.

	~\hrule~

	{\bf Step 2: Generating contrast sets from DT branches}
	\begin{itemize}
		\item Find the {\em current } cluster: take each test instance, run it down to a leaf in the DT tree.  
		\item Find the {\em desired} cluster: 
		\bi
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} clusters; i.e. leaf clusters that can be reached from level $lvl$ that are not {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\epsilon=0.5$ times the mean score of {\em current}. If none found, then repeat for $lvl += 1$
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
		\item Find the {\em delta}; i.e. the set difference between  conditions in the DT branch to {\em desired} and {\em current}. To find that delta:
		\bi
		\item
		For discrete attributes,  return the value from {\em desired}. 
		\item
		For  numerics, return the numeric difference. 
		\item
		For numerics  into ranges, return a random number selected from the low and high boundaries of the that range.
		\ei
		\ei
		~\hrule~
		\caption{CROSSTREES. Controlled by the parameters
			$\{\alpha, \beta, \gamma, \delta, \epsilon\}$ (set via engineering judgement).}
		\label{fig:xtrees_bare}
	\end{figure}

>>>>

\begin{figure}[!t] 
	\begin{shaded}
  ~\hrule~

Using the training data,  divide the data using the decision tree of algorithm of \fig{where}.D.

For each item in the test data,
	  find the {\em current } leaf: take each test instance, run it down to a leaf in the decision tree.  
After that,	  find the {\em desired} leaf:
		\begin{itemize}[leftmargin=3mm]
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\gamma=0.5$ times the mean score of {\em current}.
		 \bi
		 \item 
		   If none found, then repeat for $lvl += 1$
		 \item
		    Return no plan if the new $lvl$ is above the root.
		 \ei
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Also, find the {\em delta}; i.e. the set difference between  conditions in the decision tree branch to {\em desired} and {\em current}. To find that delta:
		\begin{itemize}[leftmargin=3mm]
		\item
		For discrete attributes,  return the value from {\em desired}. 
		\item
		For  numerics, return the numeric difference. 
		\item
		For numerics  discretized into ranges, return a random number selected from the low and high boundaries of the that range.
		\ei 
		Finally, return the delta as the plan for improving the test instance.
		~\hrule~
		\end{shaded}
		\caption{XTREES}
		\label{fig:xtrees_bare}
	\end{figure}

### 2015-08-23 tex/results_models.tex
Updates from ShareLaTeX

\begin{figure}[htbp]
\begin{center}
\begin{minipage}{\linewidth}
%\noindent\begin{minipage}{0.5\textwidth}
{\scriptsize \textbf{Cost}\\[0.1cm]}
{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &        DTREE &    0.42  &  0.17 & \quart{0}{10}{0}{20} \\
\hline  2 &      kNN+FS &    1.03  &  0.69 & \quart{30}{46}{42}{20} \\
  2 &          HOW &    1.04  &  0.01 & \quart{42}{0}{42}{20} \\
  2 &      kNN &    1.11  &  1.24 & \quart{18}{80}{46}{20} \\
\hline \end{tabular}}
\end{minipage}\\[0.1cm]
\begin{minipage}{\linewidth}
{\scriptsize \textbf{Completion}\\[0.1cm]}
{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &      kNN+FS &    0.98  &  0.01 & \quart{10}{12}{22}{22} \\
\hline  2 &          HOW &    1.0  &  0.02 & \quart{32}{22}{44}{22} \\
  2 &      kNN &    1.01  &  0.07 & \quart{0}{76}{54}{22} \\
\hline  3 &        DTREE &    1.04  &  0.03 & \quart{66}{64}{88}{22} \\
\hline \end{tabular}}
\end{minipage}
\end{center}
\caption{Results: }\label{fig:conf}
\end{figure}

>>>>

\begin{figure}[htbp]

~\hrule~

%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &        XTREES &    0.42  &  0.17 & \quart{0}{10}{0}{20} \\
\hline  2 &      CD+FS &    1.03  &  0.69 & \quart{30}{46}{42}{20} \\
  2 &          BIC &    1.04  &  0.01 & \quart{42}{0}{42}{20} \\
  2 &      CD &    1.11  &  1.24 & \quart{18}{80}{46}{20} \\
\hline 
\end{tabular}}

~\\

In this figure, {\bf 50th}
is the median value and  {\bf 25-75th} is the second and third quartile range.
The right-hand-side horizontal lines show the {\bf 50th} median value (as a black dot) in the middle
of the {\bf 25-75th} percentile range (as lines). All values here are expressed as ratios
of the median values seen in the untreated data, so {\em smaller} values are {\em better}).
A median {\bf 50th} value of
1.0 means ``no change from
baseline''; numbers less than 1.0 indicate some reduction to the baseline;
and numbers more than 1.0 indicate ``optimization failure''.
The {\bf Rank} column on the left-hand-side show the results of a statistical
analysis and results ranked ``1'' are best. Results change {\bf Rank} if they are significantly different and pass
 a post-hoc effect size test.

 ~\hrule~
\caption{Results: Methods 1,2,3,4 applied to some ground-truth data.
Values collected from   20 repeated runs of each method with different random seeds.
}\label{fig:conf}
\end{figure}
